---
title: "Activity: Street or Road?"
author: "seungjunkim"
output: html_notebook
---

## Load in the data

```{r}
library(tidyverse)
library(dplyr)
download.file(url="https://mdbeckman.github.io/dcSupplement/data/CMS_ProvidersSimple.rds",
              destfile = "Your-Name-For-The-File.rds")
DataTable <- readRDS("Your-Name-For-The-File.rds")

```

## Recreate Solved Example using `sample(50)`

```{r}

Sample <- DataTable %>% sample_n(size = 50)
pattern <- "PO BOX"
Matches <- Sample %>% filter(grepl(pattern, address))
nmatches <- Sample %>% filter(!grepl(pattern, address))

print(Matches$address)
print(nmatches$address)

```

## Recreate Soved Example using the entire `Address` data set

```{r}


Addresses <- read_csv("https://mdbeckman.github.io/dcSupplement/data/street-addresses.csv")
pattern <- "PO BOX"
Matches <- Addresses %>% filter(grepl(pattern, address))

nmatches <- Addresses %>% filter(!grepl(pattern, address))

print(Matches$address)
print(nmatches$address)

```

#### Additional Question: How many addresses are a PO BOX (including NCSU BOX)? 

```{r}

pattern <- "PO BOX|NCSU BOX"

numMatches <- Addresses %>%
  filter(grepl(pattern, address)) %>%
  nrow()


print(numMatches)




```




## Back to the Streets: Your Turn

#### Part 1: Explain (in english) each line of the following code chunk

```{r}
pattern <- "(ST|RD|ROAD)"
LeftOvers <-
  Addresses %>% 
  filter( !grepl(pattern, address),
          !grepl("\\sAPT|UNIT\\s[\\d]+$", address),
          !grepl(" BOX ", address)
          )
```
(ST|RD|ROAD) matches any occurrence of "ST", "RD", or "ROAD" in a string


- create a new dataframe called LeftOvers. It selects the rows that do not match specific patterns using for grepl() .


!grepl(pattern, address) filters out the rows where the address column does not contain the "pattern". It removes addresses that have "ST", "RD", or "ROAD" in them.


!grepl("\\sAPT|UNIT\\s[\\d]+$", address) filter out the rows"\\sAPT|UNIT\\s[\\d]+$"  It removes addresses with apartment or unit numbers.

!grepl(" BOX ", address) filters out the rows where the address column does not contain the exact pattern " BOX ". It removes addresses that include the term " BOX ".
The resulting LeftOvers dataframe contains the rows that do not match any of the specified patterns, representing the remaining addresses after filtering out the ones with road-related terms, apartment/unit numbers, and " BOX ".
#### Part 2: Implement your method on the entire `Addresses` data set. Explain how your code works line by line.

```{r}
#pattern matches any occurrence of "ST", "RD", or "ROAD" in a string
pattern <- "(ST|RD|ROAD)"

#addresses is orginal data from upper part, defined leftobers 
LeftOvers <- Addresses %>%
  # filter row based on specified ,!grepl(pattern, address) address column contains the pattern defined in the pattern variable.
  filter(!grepl(pattern, address),
  #pattern that matches either "APT" or "UNIT" , filter out row "addresses"
         !grepl("\\sAPT|UNIT\\s[\\d]+$", address),
  #filter out row "addresses" , removes addresses that include the term " BOX ".
         !grepl(" BOX ", address)
  
  
  
  )

##PO BOX" or "NCSU BOX" in a string.
pattern <- "PO BOX|NCSU BOX"

numMatches <- Addresses %>%
  #grepl(pattern, address),address column contains a match for the pattern defined in the pattern
  filter(grepl(pattern, address)) %>%
  ##calculates the number of rows.
  nrow()
```

My answer here.......

#### Additional Question 1: Present your result from part 2 by providing a table in descending order of popularity for the street name endings you found

```{r}

Addresses <- Addresses %>%
  mutate(street_ending = str_extract(address, "(ST|RD|ROAD)$"))

street_ending_counts <- Addresses %>%
  filter(!is.na(street_ending)) %>%
  count(street_ending, sort = TRUE)


street_ending_counts %>%
  arrange(desc(n))

```

#### Additional Question 2: Present your result by using ggplot to a bar chart in descending order of popularity for the street name endings you found previously.

Note: make sure your order street names according to popularity, not alphabetically.

```{r}
library(ggplot2)

Addresses <- Addresses %>%
  mutate(street_ending = str_extract(address, "(ST|RD|ROAD)$"))


street_ending_counts <- Addresses %>%
  filter(!is.na(street_ending)) %>%
  count(street_ending, sort = TRUE)

street_ending_counts <- street_ending_counts %>%
  arrange(desc(n))


ggplot(street_ending_counts, aes(x = street_ending, y = n)) +
  geom_bar(stat = "identity") +
  labs(x = "Street Name Ending", y = "Count") +
  coord_flip() +
  theme_minimal()


```

#### Additional Question 3: Comment on any patterns you see

The overall pattern observed in the bar chart suggests that certain street name endings are more commonly utilized than others, with "St," "Rd," and "Ave" being the most prevalent suffixes in the dataset. These findings offer insights into the naming conventions the streets within the dataset's coverage area.
